---
title: "HW5 Xilong Li"
author: "Xilong Li (3467966)"
date: '2022-05-15'
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidymodels)
library(tidyverse)
library(glmnet)
library(janitor) 
```

## Question 1:

```{r}
pokemon_original <- read.csv("Pokemon.csv")
pokemon <- janitor:: clean_names(dat = pokemon_original)
head(pokemon)
```
By using the "clean_names" function, the resulting names are unique and consist only of the '_' character, numbers, and letters. Capitalization preferences can be specified using the case parameter. Accented characters are transliterated to ASCII. For example, an "o" with a German umlaut over it becomes "o", and the Spanish character "enye" becomes "n".(This explanation is cited from the website: https://rdrr.io/cran/janitor/man/clean_names.html)            
## Question 2:
```{r}
copy_pokemon <- pokemon
ordered_data <- copy_pokemon %>%
  group_by(type_1) %>%
  summarise(count = n()) %>%
  arrange(count)

ggplot(ordered_data, aes(x = count, y = reorder(type_1, -count))) + geom_bar(stat = "identity")
```
As it is shown above, there are 18 classes in total, and classes such as flying, fairy, and ice have fewer pokemons than others,

```{r}
filtered_pokemon <- pokemon %>% 
  filter(type_1 %in% c("Bug", "Fire", "Grass", "Normal", "Water", "Psychic"))
final_pokemon <- filtered_pokemon %>% 
  mutate(type_1 = factor(type_1),
         legendary = factor(legendary))
dim(final_pokemon)
class(final_pokemon$type_1)
class(final_pokemon$legendary)

```

## Question 3:
```{r}
set.seed(2200)

poke_split <- initial_split(final_pokemon, prop = 0.80,
                            strata = type_1)

poke_train <- training(poke_split)
poke_test <- testing(poke_split)

poke_folds <- vfold_cv(poke_train, v = 5, strata = type_1)
class(poke_folds)
```
By stratifying the folds, we can make sure that the folds are representative of the data, since the splited data is also stratified on type_1. So that the distribution of types in each folds are approximately the same.

## Question 4:
```{r}
poke_recipe <- recipe(type_1 ~ 
                        legendary + 
                        generation + 
                        sp_atk + 
                        attack + 
                        speed + 
                        defense + 
                        hp + 
                        sp_def,
                       data = poke_train) %>% 
  step_dummy(legendary,generation) %>% 
  step_center(all_predictors()) %>%
  step_scale(all_predictors())

class(poke_train$generation)
```

## Question 5:

```{r}
poke_spec <- multinom_reg (penalty = tune(), mixture = tune()) %>%
  set_engine("glmnet")

poke_workflow <- workflow() %>% 
  add_recipe(poke_recipe) %>% 
  add_model(poke_spec)

poke_grid <- grid_regular(penalty(range = c(-5, 5)), 
                             mixture(range = c(0,1)), 
                             levels = c(10,10))
```
Thus, there will be 500 models in total, since there are ten levels each for penalty and mixture and 5 folds in the data.
## Question 6:
```{r}
poke_workflow
```


```{r}
tune_res <- tune_grid(
  poke_workflow,
  resamples = poke_folds, 
  grid = poke_grid
)
```
```{r}
autoplot(tune_res)
```


